Stable Hot Spot Analysis (Draft)

### 2017-06-16 paper-main.tex
minor fix
Removed appendix

Therefore we would calculate $10 \cdot 10 \cdot 5 + 10 \cdot 5=550$ results for each dimension.
The following conditions must hold $dim(F) > dim(W)$ and $dim(F) < dim(R)$ 
which leads e.g. to 460 results in the z-dimension.
We vary over the weight matrix W, the focal matrix F and the aggregation level, as motivated in the introduction.
To compare the impact each of these parameters has we compute all variations 
over two parameter and holding one parameter fix. We then calculate the mean as 
well as the standard deviation for the SoH for the fixed value based on the two 
other parameters. This allows us to isolate the impact of the variation in the 
single parameter. The results are then plotted in 
Figures~\ref{fig:SoHFocal}--\ref{fig:SoHZoom}, one image for each fixed 
parameter and the direction of the SoH.
The hotspots to use the SoH on are computed by the focal $G^*$ and standard $G^*$ method. The focal $G^*$ allows us, to isolate the impact that the size of the study area has on the stability of the results without recomputing the total dataset.

@@

\section{Appendix}

\subsection{Clumping}

The aggregation level is a slice plane through our three dimensional space. 
This is an example how the results can look with visualize representations of the calculated 
rasters and the raw data.
We evalute only the aggregation with fixed W and fixed F. In contrast we included the negative clusters. They where exluded for our 3 dimensional space because
the water had to much influence.
\begin{definition} Aggregation run:
\begin{eqnarray*}
    child & = & G^*(R_z, W_11, st, F_41) \\
    parent & = & G^*(R_{z+1}, W_11, st, F_41)
  \end{eqnarray*}
\begin{displaymath}
z \in [1,6], G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}

\subsection{Blur}
We also made an example for the variation of the weight size W.
Blur is a slice plane through our three dimensional space. 
W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
For blur we also included the negative clusters which resulted in a surprising result.
\begin{definition} Blur run:
\begin{eqnarray*}
    child & = & G^*(R_3, W_{7+i \cdot 2}, st, F_41) \\
    parent & = & G^*(R_3, W_{7+(i+1)\cdot 2}, st, F_41)
  \end{eqnarray*}
\begin{displaymath}
i \in [0,11], G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}
The blur results are plotted in Figure~\ref{fig:Blur}. The weight matrix is
shown in the first row, with increasing size. The scond and thrid row sho how
$G^*$ and Focal $G^*$ changes based on W. This example is a slice plane of the
weight dimension ploted in figure ~\ref{fig:SoHWeight}. It can be seen that
increase of the weight size leads in general to better results for Focal $G^*$.
$G^*$ compared to the mean of our whiskerplot does not fit in the picture
because it leads to better results than $G^*$.

>>>>

Therefore we would calculate $10 \cdot 10 \cdot 5 + 10 \cdot 5=550$ results for each dimension.
The following conditions must hold $dim(F) > dim(W)$ and $dim(F) < dim(R)$ 
which leads e.g. to 460 results in the z-dimension.
We vary over the weight matrix W, the focal matrix F and the aggregation level, as motivated in the introduction.
To compare the impact each of these parameters has we compute all variations 
over two parameter and holding one parameter fix. We then calculate the mean as 
well as the standard deviation for the SoH for the fixed value based on the two 
other parameters. This allows us to isolate the impact of the variation in the 
single parameter. The results are then plotted in 
Figures~\ref{fig:SoHFocal}--\ref{fig:SoHZoom}, one image for each fixed 
parameter and the direction of the SoH.
The hotspots to use the SoH on are computed by the focal $G^*$ and standard $G^*$ method. The focal $G^*$ allows us, to isolate the impact that the size of the study area has on the stability of the results without recomputing the total dataset. 
\subsection{Clumping}

The aggregation level is a slice plane through our three dimensional space. 
This is an example how the results can look with visualize representations of the calculated 
rasters and the raw data.
\begin{definition} Aggregation run:
\begin{eqnarray*}
    child & = & G^*(R_z, W_{11}, st, F_{41}) \\
    parent & = & G^*(R_{z+1}, W_{11}, st, F_{41})
  \end{eqnarray*}
\begin{displaymath}
z \in [1,6], G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}

\subsection{Blur}
We also made an example for the variation of the weight size W.
Blur is a slice plane through our three dimensional space. 
W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
\begin{definition} Blur run:
\begin{eqnarray*}
    child & = & G^*(R_3, W_{7+i \cdot 2}, st, F_{41}) \\
    parent & = & G^*(R_3, W_{7+(i+1)\cdot 2}, st, F_{41})
  \end{eqnarray*}
\begin{displaymath}
i \in [0,11], G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}
The blur results are plotted in Figure~\ref{fig:Blur}. The weight matrix is
shown in the first row, with increasing size. The 2nd and 3th row show how
$G^*$ and Focal $G^*$ changes based on W. This example is a slice plane of the
weight dimension ploted in figure ~\ref{fig:SoHWeight}. It can be seen that an
increase of the weight size leads in general to better results for Focal $G^*$.

@@
